Outline

### 2020-04-28 text/suppl_methods.Rmd
adding new diet categories parravicini et al. 2020

# Supplementary methods
# 1. Underwater visual census database
\noindent We used a published global database of field data collection of belt transects [@Barneche2019]. This database encompasses transect data across 585 sites in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Figure). This database only includes sites with a hard reef bottom are at the outer reef slope and were carried out at a constant depth, parallel to the reef crest. We splected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all sites. The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).

# 2. Phylogeny

# 3. Parameter estimates

@@

## 3.1. Growth parameters

### 3.1.1 Data compilation
We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF). For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e. $k_{max}$, @Morais2019]. $t0$ was kept constant at 0 for all species.

@@

### 3.1.2 Statistical analysis and extrapolation

@@

We use the R package brms to fit a bayesian phylogenetic regression model We predict log(kmax) in function of log(sizemax), sst with varying intercept per species. The intercept per species is structured by the covariance matrix.

 Family: gaussian 
  Links: mu = identity; sigma = identity 
Formula: log(kmax) ~ log(sizemax) + sstmean + (1 | phylo) 
   Data: oto (Number of observations: 496) 
Samples: 4 chains, each with iter = 2000; warmup = 1000; thin = 1;
         total post-warmup samples = 4000

Group-Level Effects: 
~phylo (Number of levels: 181) 
              Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00

Population-Level Effects: 
           Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
Intercept      0.66      0.58    -0.48     1.81       1498 1.00
logsizemax    -0.76      0.10    -0.96    -0.57       1281 1.00
sstmean        0.02      0.01    -0.00     0.05       4071 1.00

Family Specific Parameters: 
      Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
sigma     0.46      0.02     0.43     0.50       1991 1.00

Samples were drawn using sampling(NUTS). For each parameter, Eff.Sample 
is a crude measure of effective sample size, and Rhat is the potential 
scale reduction factor on split chains (at convergence, Rhat = 1).

@@

## 3.2 Body stoichiometry    
### 3.2.1 Data collection    
\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, Carribean and Palmyra. Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser. $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods. Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis (Allen et al. 1974). Elemental content was calculated based on dry mass.

### 3.2.2 Data analysis and extrapolation

@@

## 3.3 Diet stoichiometry    
### 3.3.1 Data collection 
\noindent We collected 345 adult individuals of 37 species and 12 families between 2018 and 2019 in Mo'orea and Tetiaroa, two Polynesian islands. We extracted the stomach content and stored it in a 2ml tube. After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder. Then, samples were sent to the lab (more info!!) for CNP% content analysis.

### 3.3.2 Data analysis and extrapolation  
\noindent We extracted trophic group information from ref diet paper. We constructed a simple multivariate Bayesian regression model to summarize CNP\% content data per trophic group with a random effect at the species level. This model had a Bayesian R2 of 0.61 (0.56-0.65), 0.31 (0.23-0.38), and 0.48 (0.42-0.54).           
bayes_R2(fit_cnpdiet)
     Estimate  Est.Error      Q2.5     Q97.5
R2c 0.6250538 0.02299497 0.5756378 0.6642792
R2n 0.3043510 0.03973636 0.2271046 0.3771861
R2p 0.4857449 0.03164611 0.4191740 0.5417580

\noindent We then predicted the CNP\% per diet category.

   cat    Dc_m  Dn_m  Dp_m Dc_sd Dn_sd Dp_sd
  <chr> <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>
1 1      30.6  4.13 0.424  2.88 0.865 0.197
2 2      35.1  7.96 1.50   2.71 0.857 0.193
3 3      33.1  5.79 0.751  3.52 1.06  0.242
4 4      38.1  7.45 0.879  5.14 1.60  0.360
5 5      28.9  5.10 0.619  3.35 1.03  0.239

## 3.4 Metabolic parameters    
### 3.4.1 Data collection

>>>>

# Supplementary methods

To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required (Table 1). Here, we describe how these parameters were quantified for all 1110 species in our database.

@@

## 1. Growth parameters

### 1.1 Data compilation
We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF). For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e. $k_{max}$, @Morais2019]. $t0$ was kept constant at 0 for all species.

@@

### 1.2 Statistical analysis and extrapolation

@@

@@

## 2 Body stoichiometry    
### 2.1 Data collection    
\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Carribean, and Palmyra. Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser. $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods. Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis (Allen et al. 1974). Elemental content was calculated based on dry mass.

### 2.2 Data analysis and extrapolation

@@

## 3 Diet stoichiometry    
### 3.1 Data collection 
\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian islands. We extracted the stomach content and stored it in a 2ml tube. After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder. Then, samples were sent to the lab for CNP% content analysis using similar methods as for the fish body stoichiometry.

### 3.2 Data analysis and extrapolation  
\noindent We used trophic guilds defined by Parravicini et al. (2020). We fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level. This model had a median Bayesian R2 of 0.62, 0.62, and 0.48 for C, N and P respectively.           
Next, we extracted 1000 draws of the predicted the CNP\% per trophic guild. Parravicini et al. (2020) provides the probability of reef fish species to be assigned to each of the 8 defined trophic guilds. By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database. We then took the average and standard deviation across all 1000 draws.

## 4 Metabolic parameters    
### 4.1 Data collection    
In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species. Individuals were collected using handnets and clove oil by scuba divers. After arrival in the lab, individuals were kept starved for a period of x hours/days. Then, they were held in respirometry chambers for 23 hours.

## 4.2 SMR and MMR

## 4.3 metabolic parameters

fit_mr <- brm(log10(mr) ~ 1 + log10(mass) + (0 + log10(mass)|Family) + (0 + log10(mass)|Species) + 
                (1|Family:mr_type) + (1|Species:mr_type) + (0 + log10(mass)|Family:mr_type) +
                (0 + log10(mass)|Species:mr_type), data = test,
              control = list(adapt_delta = 0.9),#, max_treedepth = 12),
              prior = set_prior(class = "b", "log10mass", prior = "normal(0.8, 0.5)"), cores = 4,
              warmup = 2000, iter = 4000)

Estimate    Est.Error      Q2.5   Q97.5
R2 0.9728325 0.0004120478 0.9719845 0.97362
